Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
A few corrections

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/list_pieces.png}}
\caption{List of blocks in the angry birds game.}
\label{piece_list}
\end{figure}
    % Explain a bit about the competition, from the introduction
The Angry Birds level generation track is a competition where the objective
is to generate levels that are \textit{fun} and \textit{enjoyable}. However,
they also have to be challenging but not impossible. The rules for the
competition specify that a configuration file must be used to generate the
levels of the game in a limited amount of time. The file contains several
restrictions; we explain each one next. The number of \textit{different}
levels that must be generated. The materials that are \textit{not allowed}.
For instance, a group of generated levels must not have circles which
composition material is ice or stone. Moreover, a material with a veto,  can
not integrate others. The third configuration value is the \textit{number of
pigs} that we must place in a level. Finally, the \textit{limit} of time
that the system has to generate the required amount of levels.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
    \caption{Structure at beginning and end of a simulation.}
    \label{test_old}
    \end{figure}

    Structures are the next evolutionary layer, at a higher level of composition.
    Structures are compositions of composites. A level can be seen as a collection 
    of structures and each structure is a pile of composite blocks. This way of 
    constructing levels has the advantage of
    limiting the search space, to structures that have a better chance to be 
    standing after the simulation ends. There is no warranty that piles of 
    composite blocks will maintain balance, so again we must search for those 
    structures.

    Structures are represented in a way similar to Togelius et al.
    \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
    an id assigned to it. A structure is then a list of ids, referring to
    composite blocks, the first 11 are basic composite and generated composites 
    are assigned a higher number.  This way and individual can be
    represented as shown on figure \ref{old_chrom} where each chromosome
    represents a certain item in the list of blocks, the numbers for this
    elements are assigned in a first come first served basis, the numbers are
    infinitely incremented and the same blocks can be repeated in a structure.

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/list_pieces.png}}
\caption{List of blocks in the angry birds game.}
\label{piece_list}
\end{figure}
    % Explain a bit about the competition, from the introduction
The Angry Birds level generation track is a competition where the objective
is to generate levels that are \textit{fun} and \textit{enjoyable}; they also have to be challenging but not impossible. The rules for the
competition specify that a configuration file must be used to generate the
levels of the game in a limited amount of time. The file contains several
restrictions; namely:\begin{itemize}
\item   The number of \textit{different}
levels that must be generated. 
\item The materials that are \textit{not allowed}.

For instance, a group of generated levels must not have spheres composed of  is ice or stone. Moreover, a banned material can
not integrate others. 
\item The third configuration value is the \textit{number of
pigs} that we must place in a level. 
\item Finally, the \textit{limit} of time
that the system has to generate the required amount of levels.
\end{itemize}

We will present next a system for evolving structures that respects those restrictions.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
    \caption{Structure at the beginning and end of a simulation.}
    \label{test_old}
    \end{figure}
    %
    Structures are the next evolutionary layer, at a higher level of composition.
    Structures are compositions of composites. A level can be seen as a collection 
    of structures and each structure is a pile of composite blocks. This way of 
    constructing levels has the advantage of
    limiting the search space to structures that have a better chance to be 
    standing after the simulation ends. There is no warranty that piles of 
    composite blocks will keep the balance, so again we must search for those 
    structures.

    Structures are represented in a way similar to Togelius et al.
    \cite{togelius2016Representationsforsearch-basedmethods}. Each block has
    an ID assigned to it. A structure is created from a list of IDs, every one of them referring to
    composite blocks; the first 11 are basic composites, while generated composites 
    are assigned a higher number.  This way and individual can be
    represented as shown on figure \ref{old_chrom} where each chromosome
    represents a certain item in the list of blocks, the numbers for these
    elements are assigned in a first come first served basis; they can be infinitely incremented. The same blocks can be repeated in a structure.
